---
title: ""
output:
  html_document:
    toc: false
---

```{r options, results='hide', echo=FALSE, message=FALSE, warning=FALSE}
if (Sys.info()["sysname"] == "Windows") {
  Sys.setlocale("LC_TIME", "english")
} else  {
  Sys.setlocale("LC_TIME", "en_US");
}
require(lubridate)
```

<div class="jumbotron">
  <h1>Information Management <br /></h1>
  <h2>Technical directions<br />
  for MENA Region</h2>
  <p>Last update : `r I(format(today(), "%e %B %Y"))`</p>
</div>


## 
<div class="alert alert-warning" style="font-weight: bold;">
## Disclaimer
  <p>The toolkit is a *collaborative effort*: if you have suggestions, please share them <a href="https://github.com/unhcr-mena/information-management-direction/issues" style="color: white;">through this link</a>.</p>
  <p>The Toolkit is a *work in progress*: if you identify issues, please share them <a href="https://github.com/unhcr-mena/information-management-direction/issues" style="color: white;">through this link</a>.</p>
</div>

## Table of Content{#tdm}


```{r tdm semi-programmatique, results='hide', message=FALSE, echo=FALSE,  warning=FALSE, include=FALSE, cache=FALSE}
base_url <- ""
urls <- paste0(base_url, "index.html")

tdm <- function(section) {
  require(xml2)
  res <- "<div class=\"row\">\n"
  
  menu <- read_html("include/before_body.html", encoding = "UTF-8")
  section <- xml_find_one(menu, paste0(".//ul[@id='menu_", section, "']"))
  sous_sections <- xml_find_all(section, ".//ul")
  
  for (ss in sous_sections) {
    res <- paste0(res, "<div class=\"col-md-4\">\n")
    titre <- as.character(xml_contents(xml_find_one(ss, ".//li[@class='dropdown-header']")))
    Encoding(titre) <- "UTF-8"
    res <- paste0(res, "<p><strong>", titre, "</strong></p>\n")
    res <- paste0(res, "<div class=\"list-group\">\n")
    
    items <- xml_find_all(ss, ".//a")
    for (item in items) {
      lien <- xml_attr(item, "href")
      titre <- as.character(xml_contents(item))
      Encoding(titre) <- "UTF-8"
      res <- paste0(res, "<a href=\"", lien,"\" class=\"list-group-item\">", titre, "</a>\n")
      urls <<- c(urls, paste0(base_url, lien))
    }

    res <- paste0(res, "</div>\n</div>\n\n")
  }
  
  res <- paste0(res, "</div>")
  return(res)
}
```


### Credits

Large parts of the toolkit are extracted from other existing guidelines referenced above. 
